\ab{Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling}

### 2021-01-06 papers/intro_paper/intro_paper.tex
changes in Section I

\documentclass[twocolumn,prd,superscriptaddress,amsfonts,amssymb,amsmath,preprintnumbers]{revtex4-1}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[dvipsnames]{xcolor}
\usepackage{bm}
\usepackage{times}
\usepackage{xspace}
\usepackage[varg]{txfonts}
\usepackage[normalem]{ulem} % To get strikethrough (\sout)
\usepackage[colorlinks]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{url}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{lineno}
\linenumbers

@@

The LIGO Scientific Collaboration~\citep{lsc} and the Virgo Collaborations~\citep{Virgo} recently announced their catalogue of gravitational wave (GW) observations~\citep{GWTC-2} from the first half of their third observing run (O3a)~\citep{O3reference}. Combined with the confirmed observations from the first and second observing runs~\citep{abbott2019gwtc}, the Advanced LIGO detectors at Hanford, Washington and Livingston, Louisiana~\citep{aasi2015characterization}, and the Advanced Virgo detector in Cascina, Italy~\citep{acernese2014advanced} have now detected more than $50$ GW events from the merger of compact objects like neutron stars and/or black holes (BHs), collectively called compact binary coalescences (CBCs). Alongside independent claims of detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020}, this has firmly established the field of GW astronomy, five years on from the first ever direct detection of GWs on Earth, on September 14, 2015~\citep{abbott2016observation}.

>>>>

\documentclass[twocolumn,prd,superscriptaddress,amsfonts,amssymb,amsmath,preprintnumbers]{revtex4-1}

\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[dvipsnames]{xcolor}
\usepackage{bm}
\usepackage{times}
\usepackage{xspace}
\usepackage[varg]{txfonts}
\usepackage[normalem]{ulem} % To get strikethrough (\sout)
\usepackage[colorlinks]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{url}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{lineno}
%\linenumbers

@@

The LIGO Scientific Collaboration~\citep{lsc} and the Virgo
Collaboration\sout{s}~\citep{Virgo} \ab{have} recently announced their catalogue of
gravitational-wave (GW) \sout{observations} \ab{signals}~\citep{GWTC-2} from the first
half of the\sout{ir} third observing run (O3a)~\citep{O3reference}. Combined
with \sout{the confirmed observations from} the first and second observing-run \ab{catalogues}~\citep{abbott2019gwtc}, the Advanced LIGO detectors at Hanford,
Washington and Livingston, Louisiana~\citep{aasi2015characterization},
and the Advanced Virgo detector in Cascina,
Italy~\citep{acernese2014advanced} have now detected \sout{more than} $50$ GW
events from the merger of compact objects like neutron stars and/or
black holes (BHs), collectively called compact binary coalescences
(CBCs). Alongside independent claims of
detections~\citep{nitz20191,nitz20202,2019PhRvD.100b3007Z,2020PhRvD.101h3030V,Venumadhav_2020},
\sout{this} \ab{these results} \sout{has} \ab{have} firmly established the field of GW astronomy, five years \sout{on
from} \ab{after} the first \sout{ever direct} detection of GWs \ab{passing through the} \sout{on} Earth, on September 14,
2015~\citep{abbott2016observation}.
